---
title: "R Notebook"
Name: Emily Curcio, Jaskaran Kohli, Xinyu (Duke) Li, Yijia Yang
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---
We separate all variable into six categories:

1. date 
2. browser, OS, device 
3. Geography
4. visits action(hits,pageviews,visit times...) 
5. channel, medium, source
6. adwords + campaign  

```{r}
rm(list=ls())
library(tidyverse)
library(jsonlite)
library(scales)
library(lubridate)
library(gridExtra)
library(data.table)
library(caTools)
library(caret)
```
#1 Loading
```{r}
train <- fread('train_flat.csv',stringsAsFactors = F)
```

```{r}
colnames(train)
dim(train)
head(train)
```
#2 Data pre-processing
##caculate NA
```{r}
is_na_val <- function(x) x %in% c("not available in demo dataset", "(not provided)",
                                  "(not set)", "<NA>", "unknown.unknown",  "(none)",'Not Socially Engaged')
```
##100% NA colnames
```{r}
colna <- apply(train, 2, function(x) sum(is_na_val(x) | is.na(x)))
colna
col_names = names(colna[colna == 903653])
col_names
```
##Remove 100% NA and subset USA
```{r}
colnames(train)
train[,(col_names):= NULL]
tr <- train[country == 'United States']
head(tr)
```
##get buy column
```{r}
#method 1
tr[is.na(transactionRevenue), buy := 0 ]
tr[!is.na(transactionRevenue), buy := 1 ]
tr[, buy := as.factor(buy)]

#method 2
#train$transactionRevenue[is.na(train$transactionRevenue)] <- 0
#train$buy[train$transactionRevenue == 0] <- 0
#train$buy[train$transactionRevenue != 0] <- 1
#as.factor(train$buy)
```
##visit action: pageview na to 0
```{r}
tr[is.na(pageviews),pageviews:=0]
```
##visit action: pageview and hits highly correlated
```{r}
cor(tr$pageviews,tr$hits)
```
##visit action: change NA in newvisits to 0
```{r}
#method 1
tr[is.na(newVisits),newVisits:=0]
tr[,newVisits := as.factor(newVisits)]
#method 2
#train$newVisits[is.na(train$newVisits)] = 0
#as.factor(train$newVisits)
```
##NA check again
```{r}
colna2 <- apply(tr, 2, function(x) sum(is.na(x)))
colna2
```
##glance
```{r}
dim(tr)
troriginal <- tr
```
##channel, medium, source: relationship bewteen medium - channel - source
medium - channel:
(none) = Direct    
affiliate =  Affiliates
cpc = Paid Search 
cpm = Display
organic = Organic Search 
referral  =  Referral +  Social 

Channel and medium are highly correlated (multicollinearity)
Source shows more specific information for each channel(medium), so it should not be a variable originally
I would choose channel as decision variable.
```{r}
#before
table(tr$medium)
table(tr$channelGrouping)
unique(subset(tr,channelGrouping == 'Social')$medium)
tr <- subset(tr,channelGrouping != '(Other)')
```
```{r}
#after remove not set
table(tr$channelGrouping)
```
##adwords + campaign: all adwords variables all belongs to Paid search
```{r}
unique(subset(tr,!is.na(adwordsClickInfo.page))$channelGrouping)
```
##adwords + campaign: campaign belongs to affilacte and paid search in Channel
```{r}
unique(subset(tr,campaign != '(not set)')$channelGrouping)
#unique(subset(tr,campaign != '(not set)')$medium)
#unique(subset(tr,campaign != '(not set)')$source)
```
so for the adwords and campaign are only relevant with partial channel, should not put into the whole model.
#3 split train test
```{r}
tr$channelGrouping <- as.factor(tr$channelGrouping)
set.seed(123)
split = sample.split(tr$buy,SplitRatio = .8)
traintr = subset(tr,split == TRUE)
testtr = subset(tr,split == FALSE)
head(traintr)
```
##check split
```{r}
table(month(tr$date))
table(month(traintr$date))
```
##weekday
```{r}
traintr$weekday <- as.factor(wday(traintr$date))
testtr$weekday <- as.factor(wday(testtr$date))
table(traintr[buy == 1]$weekday)
traintr[weekday %in% c(7),sunday:=1]
traintr[weekday %in% c(1,2,3,4,5,6),sunday:=0]
testtr[weekday %in% c(7),sunday:=1]
testtr[weekday %in% c(1,2,3,4,5,6),sunday:=0]
traintr[weekday %in% c(6,7),weekend:=1]
traintr[weekday %in% c(1,2,3,4,5),weekend:=0]
testtr[weekday %in% c(6,7),weekend:=1]
testtr[weekday %in% c(1,2,3,4,5),weekend:=0]
traintr$sunday <- as.factor(traintr$sunday)
testtr$sunday <- as.factor(testtr$sunday)
traintr$weekend <- as.factor(traintr$weekend)
testtr$weekend <- as.factor(testtr$weekend)
```
##month
```{r}
traintr$month <- as.factor(month(traintr$date))
testtr$month <- as.factor(month(testtr$date))
table(traintr[buy == 1]$month)
```
##quarter
```{r}
traintr$quarter <- as.factor(quarter(traintr$date))
testtr$quarter <- as.factor(quarter(testtr$date))
table(traintr[buy == 1]$quarter)
```
##hour
```{r}
traintr$visitStartTime <- ymd_hms(traintr$visitStartTime)
traintr$hour <- as.factor(hour(traintr$visitStartTime))
testtr$hour <- as.factor(hour(testtr$visitStartTime))
table(traintr[buy == 1]$hour)

traintr[hour %in% c(0,1,2,3,4,5,6),ampm:=0]
traintr[hour %in% 7:12,ampm:=1]
traintr[hour %in% 13:18,ampm:=2]
traintr[hour %in% 19:23,ampm:=3]
traintr$ampm <- as.factor(traintr$ampm)
testtr[hour %in% c(0,1,2,3,4,5,6),ampm:=0]
testtr[hour %in% 7:12,ampm:=1]
testtr[hour %in% 13:18,ampm:=2]
testtr[hour %in% 19:23,ampm:=3]
testtr$ampm <- as.factor(testtr$ampm)

```
##check views by channel
```{r}
tr[,.(viewsum = mean(hits)),by = channelGrouping]
```
##NA check
```{r}
traintr[is.na(traintr)] <- 0
apply(traintr, 2, function(x) sum(is.na(x)))
```
##undersampling
```{r}
library(ROSE)
undertrain <- ovun.sample(buy ~ ., data = traintr, method = "under", N = 17524, seed = 123)$data
undertrain <- as.data.table(undertrain)
table(undertrain$buy)
```
```{r}
undertrain$deviceCategory = as.factor(undertrain$deviceCategory)
head(undertrain)
```
#4 Logistic Regression Model
```{r}
undertrain$channelGrouping <- relevel(undertrain$channelGrouping,2)
#bl_result1 = glm(buy~channelGrouping, data=undertrain, family="binomial")
#bl_result2 = glm(buy~channelGrouping+hits+pageviews+newVisits, data=undertrain, family="binomial")
#bl_result3 = glm(buy~channelGrouping+hits+pageviews+newVisits+deviceCategory, data=undertrain, family="binomial")
#bl_result4 = glm(buy~channelGrouping+hits+pageviews+newVisits+deviceCategory+sunday, data=undertrain, family="binomial")
#bl_result5 = glm(buy~channelGrouping+hits+pageviews+newVisits+deviceCategory+sunday+quarter, data=undertrain, family="binomial")
#bl_result6 = glm(buy~channelGrouping+hits+pageviews+newVisits+deviceCategory+sunday+month, data=undertrain, family="binomial")
#bl_result7 = glm(buy~channelGrouping+hits+pageviews+newVisits+deviceCategory+sunday+quarter+hour, data=undertrain, family="binomial")
bl_result8 = glm(buy~channelGrouping+log(visitNumber)+log(pageviews+1)+deviceCategory+quarter+ampm, data=undertrain, family="binomial")
#summary(bl_result1)
#summary(bl_result2)
#summary(bl_result3)
#summary(bl_result4)
#summary(bl_result5)
#summary(bl_result6)
#summary(bl_result7)
summary(bl_result8)
```
##predict insample
```{r}
undertrain[,fittedval:=bl_result8$fitted.values]
a=undertrain[,.(mnfit=mean(fittedval)),by=buy]
a
```
#5 evaluation outsample 
```{r}
predTest = predict(bl_result8, testtr, type="response")
predFac <- cut(predTest, breaks=c(-Inf, 0.5, Inf),labels=c("0","1"))
confusionmatrix <- table(predFac,testtr$buy)
accuracy <- sum(diag(confusionmatrix)) / sum(confusionmatrix)
precision <- posPredValue(predFac,testtr$buy, positive="1")
recall <- sensitivity(predFac,testtr$buy,positive="1")
F1 <- (2 * precision * recall) / (precision + recall)
```
```{r}
confusionmatrix
accuracy
precision
recall
F1
```
#7 Linear Regression
```{r}
ltraintr <- subset(traintr,traintr$transactionRevenue != 0)
ltraintr
```
```{r}
ll_result9 = lm(log(transactionRevenue)~channelGrouping+log(hits+1)+log(visitNumber)+deviceCategory+sunday+ampm, data=ltraintr)
summary(ll_result9)
```



